Bayesian hidden Markov model analysis of single-molecule force spectroscopy:\\ Characterizing kinetics under measurement uncertainty

### 2015-02-16 manuscripts/bayesian-hmm-method/bhmm.tex
Updated figure 2 caption.

\begin{figure*}[tb]
\noindent
\resizebox{0.8\textwidth}{!}{\includegraphics{algorithm-workflow/Fig_ProbabilitySpace.pdf}}
\caption{{\bf Illustration of the Bayesian hidden Markov model (BHMM) sampling algorithm.}
During each BHMM update, a modified forward-backward algorithm is used to sample a new hidden state trace $\mathbf{S}$, which is then used to generate a new sample of the reversible transition matrix $\mathbf{T}$ using MCMC sampling, followed by sapling of the state emission probabilities $\mathbf{E}$.
The cycle then repeats for each subsequent iteration, which together sample from the Bayesian posterior of the HMM and fully characterize the uncertainty in the kinetic model given the data.
\label{figure:bhmm-workflow}}
\end{figure*}

>>>>

\begin{figure*}[tb]
\noindent
\resizebox{0.8\textwidth}{!}{\includegraphics{algorithm-workflow/Fig_ProbabilitySpace.pdf}}
\caption{{\bf Illustration of the Bayesian hidden Markov model (BHMM) sampling algorithm.}
During each BHMM sampling iteration, a modified forward-backward algorithm is used to sample a new hidden state trace $\mathbf{S}$, which is then used to generate a new sample of the reversible transition matrix $\mathbf{T}$ using MCMC sampling, followed by sampling new state emission probabilities $\mathbf{E}$.
Collectively, these updates sample from the Bayesian posterior of the HMM and fully characterize the uncertainty in the kinetic model given the data.
\label{figure:bhmm-workflow}}
\end{figure*}
